---
title: "Crippling and Indirect Losses from Hunting a Ground-Dwelling Game Bird"
author: "James A. Martin, Justin Rectenwald, Amanda Schmidt, Michael Hazelbaker, Holly Lott, Alex Jackson, Geoff Beane, and D. Clay Sisson"
format: html
editor: visual
---

## Abstract

## Introduction

-   \- Importance of harvest management for exploited species

-   

- Uncertainty about crippling loss


-   \- Indirect effects of hunting


-   \- Multi-state survival models

-   

- Objectives of study

## Methods

### Study Area

-    Tall Timbers <!--# Hazelbaker -->


-   LP <!--# Holly -->

-   Escape <!--# Amanda -->

-    Pineland and Jones Center <!--# Justin -->

## Results

## Discussion

### Acknowledgments

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
